\documentclass[handout]{ximera}
%\documentclass[10pt,handout,twocolumn,twoside,wordchoicegiven]{xercises}
%\documentclass[10pt,handout,twocolumn,twoside,wordchoicegiven]{xourse}

%\author{Steven Gubkin}
%\license{Creative Commons 3.0 By-NC}
\input{../preamble.tex}

\outcome{Practice on Finding the Best/Most/Least/Biggest/Smallest}
   

\title[Exercises:]{Practice on Finding the Best/Most/Least/Biggest/Smallest...}

\begin{document}
\begin{abstract}

\end{abstract}
\maketitle

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
WARNING!!! THis is NOT DONE!!!
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

  Guidelines for solving these problems:
\begin{description}
\item[1] Draw a picture (if applicable).
\item[2] Identify equations and domain.
\item[3] Get an equation in terms of a single variable.
\item[4] Use the derivative to find max/min.
\item[5] Verify that it is a max/min.
\item[6] Answer the question.
\end{description}


%%AppliedOpt1
\begin{exercise}
A farmer has 400 feet of fence available and is building a rectangular pig pen adjacent to his barn and so only needs to put fence on three sides. What dimensions yield the largest pen? Assume that the barn is sufficiently long for whatever size pen the farmer wants to build.

The shorter dimension is $\answer{100}$.  The longer dimension is $\answer{200}$
\end{exercise}


%%AppliedOpt2
\begin{exercise}
While you were fast asleep after a grueling day of hiking, your friends relocated your sleeping bag. You awake on the bank of a slow-moving river and wish to return to your campground on the opposite bank. The river is a mile wide, and your campground is a mile upriver. With no bridge in sight, you decide to swim across to some point on the opposite bank and to then walk along the bank to the campground. You can swim two miles per hour, and you can walk three miles per hour. What route will take the least amount of time?

Distance on the bank : $\answer{1-2/(\sqrt{5})}$ 

Distance in the river: $\answer{\sqrt{1+4/5}}$

\end{exercise}

%%AppliedOpt3
\begin{exercise}

\end{exercise}

%%AppliedOpt4
\begin{exercise}

	
What are the dimensions of the largest rectangle which can be inscribed in the region bounded by $\sqrt{4-x^2}$ and by the $x$-axis. Assume that the rectangle is centered.

Larger dimension is: $\answer{2\sqrt{2}}$ Shorter dimension is: $\answer{\sqrt{2}}$

\end{exercise}

%%AppliedOpt5
\begin{exercise}
	You are constructing a window in the shape of a semicircle directly atop a rectangle. If the distance around the outside of the window is to be 12 feet, what dimensions will result in the rectangular portion of the window being as large as possible?
    
    
    
\end{exercise}

%%AppliedOpt6
\begin{exercise}
You want to build a box fort with a square base, but you don't have an already-constructed box. You do, though, have 48 ft$^2$ of cardboard and a lot of duct tape, i.e. you can cut up your cardboard any way you want. What are the dimensions that will maximize the volume of your fort? Note that forts with windows are a bad idea, so you'll have to leave the top off so you can see.



\end{exercise}















\end{document}
