\documentclass[handout]{ximera}
%\documentclass[10pt,handout,twocolumn,twoside,wordchoicegiven]{xercises}
%\documentclass[10pt,handout,twocolumn,twoside,wordchoicegiven]{xourse}


%\license{Creative Commons 3.0 By-NC}
\input{../preamble.tex}

\outcome{Practice Optimization.}
   

\title[Exercises:]{Optimization Exercises to prepare for Pre-Exam 1 Presentation}

\begin{document}
\begin{abstract}
  Here we'll practice solving optimization problems.  Be ready to present any of these problems by Monday Feb 6th with your group.  Focus on presenting your work in a clear, logical, easy-to-follow manner and fully justify your answer using CALCULUS!!!!
\end{abstract}
\maketitle

%%OPTIMIZATION 1
\begin{exercise}
  Find the dimensions of the rectangle of largest area having fixed
  perimeter $100$.

  \[
  \answer{25}\times \answer{25}
  \]

\end{exercise}

%%OPTIMIZATION 2
\begin{exercise}
 Find the dimensions of the rectangle of smallest perimeter with fixed area $100$.
  \[
  \answer{10}\times \answer{10}
  \]

\end{exercise}

%%OPTIMIZATION 3
\begin{exercise}
A box with square base and no top is to hold a volume $100$.  Find
  the dimensions of the box that requires the least material for the
  five sides.

  \[
  \text{width}=\answer{2\cdot 5^{2/3}},\qquad
  \text{length}=\answer{2\cdot 5^{2/3}},\qquad
  \text{height}=\answer{5^{2/3}}
  \]

\end{exercise}

%%OPTIMIZATION 4
\begin{exercise}
A box with square base is to hold a volume $200$. The bottom and top
  are formed by folding in flaps from all four sides, so that the
  bottom and top consist of two layers of cardboard.  Find the
  dimensions of the box that requires the least material.

  \[
  \text{width}=\answer{100^{1/3}},\qquad
  \text{length}=\answer{100^{1/3}},\qquad
  \text{height}=\answer{2\cdot 100^{1/3}}
  \]

\end{exercise}

%%OPTIMIZATION 5
\begin{exercise}
A box with square base and no top is to hold a volume $V$.  Find (in
  terms of $V$) the dimensions of the box that requires the least
  material for the five sides.

  \[
  \text{width}=\answer{2^{1/3}V^{1/3}},\qquad
  \text{length}=\answer{2^{1/3}V^{1/3}},\qquad
  \text{height}=\answer{V^{1/3}/2^{2/3}}
  \]

\end{exercise}

%%OPTIMIZATION 6
\begin{exercise}
You have $100$ feet of fence to make a rectangular play area
  alongside the wall of your house.  The wall of the house bounds one
  side.  What is the largest size possible (in square feet) for the
  play area?

  \[
  \answer{1250} square feet
  \]

\end{exercise}









\end{document}
